%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {PhD in Computer Graphics and Virtual Reality} % Degree
    {Chung Ang University} % Institution
    {Seoul, South Korea} % Location
    {August 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Currently pursuing doctoral degree at Virtual Environments Lab, Graduate school of advanced imagining science, Chung Ang University, Seoul, South Korea.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Master of Technology (M.Tech) in Computer Networks and Engineering} % Degree
    {The oxford College of Engineering, VTU} % Institution
    {Bengaluru , India} % Location
    {August. 2011 - June. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {A dissertation on "Interoperability issues between WiMAX and LTE"  submitted in partial fulfillment of the requirements for the degree of master of technology.}
         \item {Got acquainted with Network Simulators (NS2 and NS3).}
        \item {Secured First Class with Distinction. (74.25 \%) }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Bachelor of Engineering (B.E) in Information Science} % Degree
    {A.P.S College of Engineering, VTU} % Institution
    {Bengaluru, India} % Location
    {September. 2007 - June. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
          \item {A dissertation on "Design and Implementation of an Energy aware routing protocol for Wireless Sensor Networks (WSN)" submitted in partial fulfillment of the requirements for the bachelor degree of engineering.}
        \item {Secured First Class. (64.5 \%)}
      \end{cvitems}
    }

%---------------------------------------------------------
  %\cventry
   % {Licentiate degree in Business Administration} % Degree
   % {National University of Cordoba} % Institution
    %{Cordoba, Argentina} % Location
    %{Jan. 2014 - Dec. 2018} % Date(s)
    %{
      %\begin{cvitems} % Description(s) bullet points
        %\item {Standard bearer at UNC FCE. GPA: 9.53/10 (highest GPA award). %Passed subjects: 42/42}
      %\end{cvitems}
    %}
%---------------------------------------------------------

\end{cventries}
