%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Scholar} % Job title
    {Virtual Environments Lab, GSAIM} % Organization
    {Seoul, South Korea} % Location
    {Aug. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Currently working as a research scholar and pursuing full time PhD.}
        \item {Working on a research project “Proxemics based pervasive Interactions for the wide-area and high-speed serial motion recognition”, supported by Institute of Information \& Communication Technology Planning and Evaluation grant funded by the Republic of Korea government. }
        \item {Have developed an indigenous human motion authoring and editing system.}
        \item {Have involved continuously in research article publications and have attended several conferences and knowledge exchange programs.}
        \item {Have made contributions to open-source projects (Github) such as Visualization Toolkit (VTK) supported by Kitware Technologies®}
        \item {Have actively involved in research article reviews.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Assistant Professor} % Job title
    {Department of ISE, Jyothy Institue of Technology} % Organization
    {Bengaluru, India} % Location
    {July. 2015 - July. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Immaculately led and coordinated a technical forum - "Graphics Day". Also, organized several technical talks, workshops and faculty development programs. }
        \item {Have played a key role in developing and maintaining Jyothy Institute's official websites.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Assistant Professor} % Job title
    {Department of ISE, APS College of Engineering} % Organization
    {Bengaluru, India} % Location
    {June. 2013 - July. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led and organized technical forum of ISE department – “Tech-Spark” and "SPARKUP-2014"}
        \item {Worked as a placement co-ordinator at department of placement \& training, and gained experience in conducting various on campus \& pool campus drives.}
      \end{cvitems}
    }

\end{cventries}
