%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Technical Talks}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {UIT-RGPV} % Degree
    {Blockchain and Internet of Things} % Institution
    {Bhopal, Madhya Pradesh, India} % Location
    {31st July 2021} % Date(s)
    {AICTE Training and Learning (ATAL) Academy Sponsored Faculty Development Program, organized by Department of Computer Science and Engineering.}
    
    
    \cventry
    {BNMIT} % Degree
    {Blockchain of Things} % Institution
    {Bengaluru, Karnataka, India} % Location
    {18th January 2021} % Date(s)
    {AICTE Training and Learning (ATAL) Academy Sponsored Faculty Development Program, organized by Department of Computer Science and Engineering.}
    
    \cventry
    {Sona College of Technology} % Degree
    {Challenges and Research Directions for Blockchains} % Institution
    {Salem, Tamilnadu, India} % Location
    {10th Febraury 2021} % Date(s)
    {AICTE Sponsored Faculty Development Program, organized by Department of Computer Science and Engineering.}
    
    \cventry
    {RR Institue of Technology} % Degree
    {Human Computer Interaction in Virtual Environments} % Institution
    {Bengaluru, Karnataka, India} % Location
    {17th August 2020} % Date(s)
    {Faculty Development Program, organized by Department of Computer Science and Information Science Engineering.}
    
    \cventry
    {Sri Venkateshwara College of Engineering} % Degree
    {Mobile App Development using Android Studio - Hands-on Session} % Institution
    {Bengaluru, Karnataka, India} % Location
    {24th Febraury 2018} % Date(s)
    {Indian Society For Technical Education sponsored Student Development Program, organized by Department of Computer Science and Engineering.}
    
     \cventry
    {Dr. AIT} % Degree
    {IOT and its Applications} % Institution
    {Bengaluru, Karnataka, India} % Location
    {1st March 2017} % Date(s)
    {Student Development Program, organized by Department of Computer Applications.}
    
    \cventry
    {BMS College of Engineering} % Degree
    {Opportunities in the field of IOT} % Institution
    {Bengaluru, Karnataka, India} % Location
    {6th March 2017} % Date(s)
    {Technical Education Quality Improvement Programme of Government of India Sponsored Student Development Program, organized by Department of Computer Science and Engineering.}
    
    \cventry
    {Sir M Visvesvaraya Institute Of Technology} % Degree
    {Programming and Application Development using Python} % Institution
    {Bengaluru, Karnataka, India} % Location
    {11th March 2017} % Date(s)
    {Student Development Program Organized by Department of Computer Applications.}
    
    
\end{cventries}
